Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
too much passive form in this subsection
this subsection needs a box-a-whisker plot of ratings
comment on similarity of the histogram of expert ratings

>>>>

\vl{Too much passive form in this subsection. @writing}

\vl{This subsection needs a box-and-whisker plot of ratings, where the 143 different
couples of instrument and playing techniques are sorted on the x-axis by average rating. @figure @ratings}

\vl{Are the histogram of ratings similar for the two raters? It would be good to make a statistical test for this. @research @stats @ratings}
